Response to Reviewers

### 2021-11-13 Scripts/Initial_Analysis.Rmd
First draft of responses to Rev 1

top_stocks_per_country <- Eme_Res %>% 
  rename(geo_region = un_sub_region) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,geo_region,tresh,taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  group_by(sau_fishing_entity,geo_region,tresh,variable) %>% 
  # Select top 5 most valuable stocks
  top_n(5,value)

@@

Prop_results %>% 
  filter(variable == "n_per") %>% 
  group_by() %>% 
  summarise_at(vars(early,mid),funs(
    median(.,na.rm=T),
    sd(.,na.rm=T),
    length(unique(eez_name)),
    length(unique(eez_name))/280*100
  )
  )

@@

# Estimate the percentage changing
n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>%
  select(eez_name,early,mid) %>% 
  left_join(n_trans_eez) %>% 
  # mutate(per = (early/n_trans)*100) %>% 
  mutate_at(vars(early,mid),
            .funs = ~(./n_trans)*100) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  select(sau_fishing_entity,fishing_entity_id,early,mid) %>% 
  gather("time_step","avrg_spp_per",early:mid) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,time_step) %>%
  summarise(avrg_spp_per = mean(avrg_spp_per,na.rm=T)) %>% 
  mutate(time_step = ifelse(time_step == "early","per_early","per_mid")) %>% 
  mutate(avrg_spp_per = ifelse(avrg_spp_per > 50,50,avrg_spp_per))

@@

time_sets <- c("per_early","per_mid")
# i = 1
for(i in 1:2){
  gc()# clean ram

@@

  Prop_map <- ggplot() +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
    geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_point(data = subset(Map_data, variable =="mean_eez" & time_step == time & per_plot < 0), 
               aes(start_lon,
                   start_lat
               ),
               size = 0.05,
               col = "gray80",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(paths, variable =="mean_eez" & time_step == time & per_plot > 0), # filter data 
              aes(X,
                  Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 0.3,
              lineend = "round",
              arrow = arrow(length = unit(0.008, "npc"),
                            ends = "first"),
              show.legend = NA) +
    # Closeup Rectangles 
    # geom_rect(data=Rectangles,
    #           aes(xmin=x1, 
    #               xmax=x2,
    #               ymin=y1,
    #               ymax=y2),
    #           color="grey50", 
    #           fill = NA,
    #           linetype = "dashed"
    # ) +
    my_ggtheme_m(leg_pos = "bottom") +
    scale_colour_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # option="magma",
      # direction = -1
    ) +
    scale_fill_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # alpha = 0.8
      # option="magma",
      # direction = -1
    ) #+
  # ggsave("./Figures/fig_sup_1.png",
  # width = 12,
  # height = 8,
  # units = "in"
  # )

@@

@@

@@

top_rop_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = World_map, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
  geom_point(data = subset(top_map_data, variable =="mean_eez" & time_step == time & per_plot < 0), 
             aes(start_lon,
                 start_lat
             ),
             size = 0.05,
             col = "gray80",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(top_paths, variable =="mean_eez" & time_step == time & per_plot > 0), # filter data 
            aes(X,
                Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 0.9,
            lineend = "round",
            arrow = arrow(length = unit(0.008, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_colour_viridis(
    name= "Changes in catch proportion",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10),
    labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
  ) + guides(
      color=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

ggsave(
  plot = top_rop_map,
  filename = "./Figures/top_ssr.png",
  width = 12,
  height = 8,
  units = "in"
)

>>>>

top_stocks_per_country <- Eme_Res %>% 
  rename(geo_region = un_sub_region) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,geo_region,tresh,taxon_key) %>% 
  summarise(n()) %>% 
  left_join(Sau_data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(!is.na(variable)) %>% 
  group_by(sau_fishing_entity,geo_region,tresh,variable) %>% 
  # Select top 5 most valuable stocks
  top_n(5,value) %>% 
  left_join(Exploited_spp_list)

@@

### Median number of stocks changing in each time step
Prop_results %>% 
  filter(variable == "n_per") %>% 
  group_by() %>% 
  summarise_at(vars(early,mid),funs(
    median(.,na.rm=T),
    sd(.,na.rm=T),
    length(unique(eez_name)),
    length(unique(eez_name))/280*100
  )
  )

@@

# Estimate the percentage changing
n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>%
  select(eez_name,early,mid) %>% 
  left_join(n_trans_eez) %>% 
  # mutate(per = (early/n_trans)*100) %>% 
  mutate_at(vars(early,mid),
            .funs = ~(./n_trans)*100) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  select(sau_fishing_entity,fishing_entity_id,early,mid) %>% 
  gather("time_step","avrg_spp_per",early:mid) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,time_step) %>%
  summarise(avrg_spp_per = mean(avrg_spp_per,na.rm=T)) %>% 
  mutate(time_step = ifelse(time_step == "early","per_early","per_mid")) %>%
  mutate(avrg_spp_per_100 = avrg_spp_per,
    avrg_spp_per = ifelse(avrg_spp_per > 50,50,avrg_spp_per))

# Paper numbers for Rev. 1

n_taxa_data %>% 
  group_by(time_step) %>% 
  summarise_at(vars(avrg_spp_per),
               c(mean,sd,min,max),
               na.rm=T)

@@

time_sets <- c("per_early","per_mid")
i = 1
for(i in 1:2){
  gc()# clean ram

@@

  Prop_map <- ggplot() +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
    geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2
    geom_point(data = subset(Map_data, variable =="mean_eez" & time_step == time & per_plot < 0), 
               aes(start_lon,
                   start_lat
               ),
               size = 0.05,
               col = "gray80",
               shape = 20,
               stroke = 1.5) +
    geom_path(data = subset(paths, variable =="mean_eez" & time_step == time & per_plot > 0), # filter data 
              aes(X,
                  Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 1,
              lineend = "round",
              arrow = arrow(length = unit(0.008, "npc"),
                            ends = "first"),
              show.legend = NA) +
    my_ggtheme_m(leg_pos = "bottom") +
    scale_colour_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # option="magma",
      # direction = -1
    ) +
    scale_fill_viridis(
      name= "Changes in catch proportion \nand changing stocks (%)",
      limits = c(0,max(Map_data$per_plot)),
      breaks = seq(0,max(Map_data$per_plot),10),
      labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
      # alpha = 0.8
      # option="magma",
      # direction = -1
    ) #+

  ggsave(
    plot = Prop_map,
    filename = "./Figures/fig_5n.png",
    width = 10,
    height = 5,
    units = "in"
  )

@@

top_prop_results %>% 
  filter(variable == "n_per") %>% 
  group_by() %>% 
  summarise_at(vars(early,mid),funs(
    median(.,na.rm=T),
    sd(.,na.rm=T),
    length(unique(eez_name)),
    length(unique(eez_name))/280*100
  )
  )

@@

View(top_data)

@@

top_rop_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(World_map,sovereignt != "Antarctica"), size = 0.1, fill = "grey50", col = "gray30") + # created for figure 2

  geom_point(data = subset(top_map_data, variable =="mean_eez" & time_step == time & per_plot < 0), 
             aes(start_lon,
                 start_lat
             ),
             size = 0.05,
             col = "gray80",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(top_paths, variable =="mean_eez" & time_step == time & per_plot > 0), # filter data 
            aes(X,
                Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 0.9,
            lineend = "round",
            arrow = arrow(length = unit(0.008, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_colour_viridis(
    name= "Changes in catch proportion",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10),
    labels = c(seq(0,max(Map_data$per_plot-10),10),">50")
  ) + guides(
      color=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

ggsave(
  plot = top_rop_map,
  filename = "./Figures/top_ssr.png",
  width = 10,
  height = 5,
  units = "in"
)

### 2021-11-13 Scripts/Manuscript.Rmd
First draft of responses to Rev 1

**While the total number of shifting stocks is important for fisheries management, having high-valuable stocks shifting sooner could be a much bigger concern than having many low-value stocks shifting. Thus, we looked at the year of range shift of the top five most valuable transboundary stocks of each country (New Fig 4). On average, countries are projected to see a range shift of the top five most valuable stocks by 2038 $\pm$ 25 years under threshold two( 2028 $\pm$ 22 years under threshold one). Moreover, our projections suggest that these high value stocks are already shifting in 52 (27%) coastal nations under threshold two (n = 85 44% under threshold one), with the regions of Latin America and the Caribbean (n = 63), Sub-Saharan Africa (n = 59), South-eastern Asia  (n = 28), and Polynesia (n = 19) presenting the larger number of shifting stocks (25% of total high value stocks).**

@@

```{r toeFigure3, eval = T,  echo = F, fig.width=8, fig.height=6, fig.pos= "H", fig.cap =  "Average range shift of transboundary stocks and corresponding fishing revenue per country. Countries are coded according to different colored symbols representative of 5 distinct regions. The horizontal line separates countries above and below the 75th percentile of annual fishing revenue. Showing country names for the eleven nations above the 75th percentile and projected to have an average shift across transboundary stocks within its EEZ within 5 years of the 2030 Agenda deadline."}

@@

>>>>

**While the total number of shifting stocks is important for fisheries management, having high-valuable stocks shifting sooner could be a much bigger concern than having many low-value stocks shifting. Thus, we looked at the year of range shift of the top five most valuable transboundary stocks of each country (New Fig 4). On average, countries are projected to see a range shift of the top five most valuable stocks by 2038 $\pm$ 25 years under threshold two (2028 $\pm$ 22 years under threshold one). Moreover, our projections suggest that these high value stocks are already shifting in 52 (27%) coastal nations under threshold two (n = 85 44% under threshold one), with the regions of Latin America and the Caribbean (n = 63), Sub-Saharan Africa (n = 59), South-eastern Asia  (n = 28), and Polynesia (n = 19) presenting the larger number of shifting stocks (25% of total high value stocks).**

@@

```{r toeFigure3, eval = T,  echo = F, fig.width=8, fig.height=6, fig.pos= "H", fig.cap =  "Year of change in the shared distribution of the top five most valuable transboundary stocks of each country. EEZs with no distributional shift between 2006 and 2100 are represented in pale blue."}

@@

**Most EEZs are expected to see a relative small number of stocks shifting their SSR (Fig. \@ref(fig:toeFigure4)A). On average, EEZs are expected to see changes in SSR on 16% $\pm$ 10 of transboundary stocks increasing to 20% $\pm$ 11 by mid of the $21^{st}$ century. However, this result masks mask large variation in changes across EEZs. By early century, the EEZs of French Guiana (54%), South Africa (59%), Falkland Isl. (61%), Brazil (75%) and Kerguelen Isl., and Pitcairn (both 100%) are projected to see changes in SSR of over 50% in their transboundary stocks. On the other hand, some island territories such as Anguilla are projected to see changes in as low as 2% of their transboundary stocks.**

**Shifts in the SSR of the top 5 most valuable transboundary stocks of each country are projected to be 61 $\pm$ 18% by 2030 and 72 $\pm$ 17% by 2050 in 83% of the world's EEZs (Figure SX). In some cases, the SSR of one EEZ is projected increase in more than double relative to their neighbors (e.g., from 10% to 30% SSR). Some of these EEZs include Guatemala gaining from Mexico in the Pacific, Cyprus from Greece and Turkey in the Mediterranean Sea, and Russia from Norway and Japan in the Barents Sea and Western Pacific, respectively**

### 2021-11-13 Scripts/responses_rev_gcb.Rmd
First draft of responses to Rev 1

Major comments:
I am concerned about the lack of a clear definition of “fish stock” in this manuscript, since it is absolutely central to the analysis. I cannot find where in the manuscript the definition of stocks is laid out. In most literature (and especially in fisheries science), stocks have a specific (if flexible) definition as populations of a species with some degree of demographic isolation from other stocks, such that the population dynamics of separate stocks may be considered independent. In this manuscript, it seems that instead, a transboundary stock is simply defined as any pair of EEZs that share a species distribution. I would recommend that the authors define the precise definition of fish stock explicitly within the manuscript, including how their definition is different from the definition in other, related literature.

@@

    - Methods Line XX, *Let us consider the transboundary species Atlantic cod (*Gadus morhua*) as an example. Atlantic cod's distribution in the Northwest Atlantic ranges from the United States to Greenland. Based on the previous definition of a transboundary stock, the United States and Canada share a stock of Atlantic cod, and Canada and Greenland share a separate stock of Atlantic cod, but the United States and Greenland do not share a stock as they do not have juxtaposing EEZs.*

@@

- **Response:** We agree with the reviewer that and un-weighted centroid can severely skew the actual distribution of the species and influence our results. We have revised the manuscript to clarify that we did account for the heterogeneous distribution of fish stocks across their entire range. The geographic centroid of each stock is indeed weighted by the abundance of the stock. The DBEM uses the species probability of occurrence to estimate the biomass of the species at each 0.5 x 0.5 gridcell as indicated from lines XX to XX of the methods. The centroid of a transboundary stock was determined by the average latitude and longitude ($lon_{ts}$) of the grid cells holding the specified percentile ($per^{th}$) of the projected transboundary stock abundance (see below). This is, we determined the centroid of the stock using only those regions where abundance was higher (i.e., using the probability of occurrence of the DBEM). Moreover, we estimated the sensitivity of our results to the (arbitrarily) $per^{th} = 95^{th}$ percentile threshold as described in lines XX and shown in Figure S6 of the supplements. It reads as follows in line XX:

@@

- **Response:   (INCOMPLETE)** This is a very good observation and we believe it has increased the impact of our manuscript. We have included two new figures (**Supplement Figures XX and XX**) showing the average range shift and SSR of the top 5 most valuable transboundary stocks per country (Please note that figure 4 has been removed from the revised manuscript).

  - Range shift, line XX: *Having high-valuable stocks shifting sooner could be a much bigger concern than having many low-value stocks shifting. On average, countries will see a range shift of the top 5 most valuable stocks by 2038 $\pm$ 16 years (Figure S-NEW). Moreover, our projections suggest that these high value stocks are already shifting in 66% of coastal nations, with the regions of Polynesia (n = 22), Sub-Saharan Africa (n = 36) and Latin America and the Caribbean (n = 62) presenting the larger number of shifting stocks (20% of total high value stocks).*

@@

- SSR , line XX: **

![Top 5](../Figures/top_ssr.png)

Specific comments:

Abstract:
Line 10: what does this line mean: “showing early, and sometimes past shifts”?

@@

Introduction:
Be careful of verb tense. The Introduction mixes past with present tense. For example, the first two sentences starting at Line 57.

- **Response: (INCOMPLETE)** Many thanks for this observation. We have revised the whole manuscript to be sure verb tense is maintained through the document.

Methods:

@@

- **Response:** This is indeed the definition of our stock. We do not deferenciate between transboundary and straddling stocks as per defined in Palacios-Abanes *et al.* (2020). Please refer to our responses to the main comment.

@@

- **Response:** Thank you for your concern. In short the answer is yes, an EEZ could both lose and gain SSR of the same *species* but not of the same *stock.* This is because, according to our definition of stock, a species who spans multiple EEZs has multiple stocks (see response to the previous question and the main comment). let us use the Peruvian anchoveta (*Engraulis ringens*) as an example.

Peru has identified two main stocks of Peruvian anchoveta. one in the central/norther part of the EEZ and one in the south, shared with Chile. Although the northern stocks is not considered transboundary [@Cashion:2018cg; @PalaciosAbrantes:2020tv] and Equador hardly ever reports anchoveta landings (wwww.searaundus.org), in some few years, environmental variability has pushed the central/north stock towards the EEZ of Ecuador. In those years one could argue that, the Peruvian anchoveta SSR of Peru-Ecuador favors Ecuador.

At the same time, there are regional concerns that the Peruvian southern stock of anchoveta, shared with Chile, has been slowly shifting south into Chilean waters to the point that these two nations are now pushing towards cooperative management of such stock. In this case, the SSR of Peru-Chile, favors Chile.

This is only and example as our study is not capable of capturing this specific nuisance since we are not able to differentiate stocks within an EEZ nor more detailed, local, environmental factors (in this case, for example, the Humboldt current). However, we believe this

Results:

@@

- **Response:NOTE THINKING ON CHANGEING FIGURES** Our original intention was to show the importance in terms of value, of shifting stocks. However, we agree that this figure is confusing and it's message was ambiguous. Moreover, we think that the reviewers suggestion of the most valuable species brings home a mor important message and have decided to remove this figure from the revised manuscript and include the "top 5 most valuable stocks" figure instead.

@@

@@

Discussion

>>>>

## Major comments:
I am concerned about the lack of a clear definition of “fish stock” in this manuscript, since it is absolutely central to the analysis. I cannot find where in the manuscript the definition of stocks is laid out. In most literature (and especially in fisheries science), stocks have a specific (if flexible) definition as populations of a species with some degree of demographic isolation from other stocks, such that the population dynamics of separate stocks may be considered independent. In this manuscript, it seems that instead, a transboundary stock is simply defined as any pair of EEZs that share a species distribution. I would recommend that the authors define the precise definition of fish stock explicitly within the manuscript, including how their definition is different from the definition in other, related literature.

@@

  - Methods Line XX, *Let us consider the transboundary species Atlantic cod (Gadus morhua) as an example. Atlantic cod's distribution in the Northwest Atlantic ranges from the United States to Greenland. Based on the previous definition of a transboundary stock, the United States and Canada share a stock of Atlantic cod, and Canada and Greenland share a separate stock of Atlantic cod, but the United States and Greenland do not share a stock as they do not have juxtaposing EEZs.*

@@

- **Response:** We agree with the reviewer that and un-weighted centroid can severely skew the actual distribution of the species and influence our results. We have revised the manuscript to clarify that we did account for the heterogeneous distribution of fish stocks across their entire range. Specifically, the geographic centroid of each stock is indeed weighted by the abundance of the stock. The DBEM uses the species probability of occurrence to estimate the biomass of the species at each 0.5 x 0.5 gridcell as indicated from lines XX to XX of the methods. The centroid of a transboundary stock was determined by the average latitude and longitude ($lon_{ts}$) of the grid cells holding the specified percentile ($per^{th}$) of the projected transboundary stock abundance (see below). This is, we determined the centroid of the stock using only those regions where abundance was higher (i.e., using the probability of occurrence of the DBEM). Moreover, we estimated the sensitivity of our results to the (arbitrarily) $per^{th} = 95^{th}$ percentile threshold as described in lines XX and shown in Figure S6 of the supplements. It reads as follows in line XX:

@@

- **Response:** This is a very good observation and we believe it has increased the impact of our manuscript. We have included two new figures (**Figure 4** and **Figure SXX**) showing the average range shift of the top 5 most valuable transboundary stocks per country (Please note that the old figure 4 has been removed from the revised manuscript, see response to the Fig. 4 comment, below).

  - Range shift, line XX: *Having high-valuable stocks shifting sooner could be a much bigger concern than having many low-value stocks shifting. On average, countries will see a range shift of the top 5 most valuable stocks by 2038 $\pm$ 16 years (Figure SXX). Moreover, our projections suggest that these high value stocks are already shifting in 66% of coastal nations, with the regions of Polynesia (n = 22), Sub-Saharan Africa (n = 36) and Latin America and the Caribbean (n = 62) presenting the larger number of shifting stocks (20% of total high value stocks).*

@@

## Specific comments:

### Abstract:
Line 10: what does this line mean: “showing early, and sometimes past shifts”?

@@

### Introduction:
Be careful of verb tense. The Introduction mixes past with present tense. For example, the first two sentences starting at Line 57.

- **Response: (INCOMPLETE)** Many thanks for this observation. We have revised the whole manuscript to be sure verb tense is maintained through the document. 
### Methods:

@@

- **Response:** This is indeed the definition of our stock. We do not differentiate between transboundary and straddling stocks as per defined in Palacios-Abanes *et al.* (2020). Please refer to our responses to the main comment.

@@

- **Response:** Thank you for your concern. In short the answer is yes, an EEZ *could* both lose and gain SSR of the same *species* but not of the same *stock.* This is because, according to our definition of stock, a species who spans multiple EEZs has multiple stocks (see response to the previous question and the main comment). Please refer above to our response to the question *How does the choice of stock definition influence the calculation of SSR?*

### Results:

@@

- **Response:NOTE THINKING ON CHANGING FIGURES** Our original intention was to show the importance in terms of value, of shifting stocks. However, we agree that this figure is confusing and it's message was ambiguous. Moreover, we think that the reviewer's suggestion of the most valuable species brings home a more important message and have decided to remove this figure from the revised manuscript and include the "top 5 most valuable stocks" figure instead.

@@

- **Response:**  Thank you for your comment. See below responses to both parts of the question.

Fig. 5- this figure is hard to read,

- **Response:** We agree with the reviewer that this figure is quite busy and have divided the figure in two. Figure 5 is now just panel A while the regional zooms were sent to the supplemental material. We believe that the arrows are now easier to appreciate.

![New Figure 5](../Figures/Fig5n.png)

![New Figure SX for regional](../Figures/Fig5SX_ssr)

and is another figure that may be misleading if not weighted by abundance or value. It is strange to “average” across a unitless ratio (SSR).

- **Response:** We would like to clarify here that that the Stock Share Ratio (SSR) is not unit less. It represents the percentage of the shared distribution of a stock that each EEZ has. So for example, Canada and the US share Pacific halibut the SSR for Canada is 20% and that of the US is 80%, meaning that Canada holds 20% of the distribution of the stock within its waters and the US the other 80%. We have modified the methods to make sure this is clearer now:

  - - *This way, if, Canada and the US share a specific stock the SSR for Canada could be 20% and that of the US 80%, meaning that Canada holds 20% of the distribution of the stock within its waters and the US the other 80%.*

For example, a country could “gain” a small share of an extremely high-value species, perhaps enough to offset economically a number of losses of smaller or less valuable stocks. However, in the figure, the “average” SSR for that country would be negative (arrow going out). The authors should distinguish (in the text and in this figure) different possible situations like this.

- **Response:** Yes, we agree with the reviewer and just like for Fig. 3, believe including a figure of high-value stocks will increased the impact of our manuscript. We have included such figure in the supplements and the following text in the results section:

- line XX: **Shifts in the SSR of the top 5 most valuable transboundary stocks of each country are projected to be 61 $\pm$ 18% by 2030 and 72 $\pm$ 17% by 2050 in 83% of the world's EEZs (Figure SX). In some cases, the SSR of one EEZ is projected increase in more than double relative to their neighbors (e.g., from 10% to 30% SSR). Some of these EEZs include Guatemala gaining from Mexico in the Pacific, Cyprus from Greece and Turkey in the Mediterranean Sea, and Russia from Norway and Japan in the Barents Sea and Western Pacific, respectively**

![Top 5](../Figures/Fig5SXX_top.png)

@@

- **Response:** We show that result in Figure 5 in the land polygon as the percentage of stocks that are changing but realize we did not include an in-text description of the result. It now reads on line XX:

  - - **Most EEZs are expected to see a relative small number of stocks shifting their SSR (Fig. \@ref(fig:toeFigure4)A). On average, EEZs are expected to see changes in SSR on 16% $\pm$ 10 of transboundary stocks increasing to 20% $\pm$ 11 by mid of the $21^{st}$ century. However, this result masks large changes, specially on island territories. By early century, the EEZs of French Guiana (54%), South Africa (59%), Falkland Isl. (61%), Brazil (75%) and Kerguelen Isl., and Pitcairn (both 100%) are projected to see changes in SSR of over 50% in their transboundary stocks. On the other hand, some island territories such as Anguilla are projected to see changes in as low as 2% of their transboundary stocks.**

### Discussion
